---
title: "R Notebook"
output: html_document
---

From Data is Plural:
https://docs.google.com/spreadsheets/d/1wZhPLMCHKJvwOkP4juclhjFgqIY8fQFMemwKL2c64vk/edit#gid=0

Danish zoologist Anders Pape Møller counted the number of insects killed on the windscreen of a single car after each of 1,375 journeys along the same stretch of road between 1997 and 2017. After accounting for time of day, weather, and other factors, Møller says his data suggests an 80% decline in flying insects during that time. Related: The Guardian on two bug-splat studies, including Møller’s. [h/t Laura Norén and Brad Stenger]
Møller, Anders Pape, AgroParisTech
https://doi.org/10.5061/dryad.gq73493

Tutorials to follow:
https://www.datanovia.com/en/blog/gganimate-how-to-create-plots-with-beautiful-animation-in-r/
https://rpubs.com/deepansha14/animated_timeseries_plot
```{r}
library(dplyr)
library(ggplot2)
bugs_data <- read.csv(file = "Day15_bugs/bugs.csv", header = TRUE)
```
position the caret at any line or the code chunk, then click "+".

The code chunk appears:
```{r}
```

Type any R code in the chunk, for example:
```{r}
mycars <- within(mtcars, { cyl <- ordered(cyl) })
mycars
```

Now, click the **Run** button on the chunk toolbar to [execute](https://www.jetbrains.com/help/pycharm/r-markdown.html#run-r-code) the chunk code. The result should be placed under the chunk.
Click the **Knit and Open Document** to build and preview an output.