---
title: "R Notebook"
output: html_document
---

Source of data: Heinz G, Peterson LJ, Johnson RW, Kerk CJ. 2003. Exploring Relationships in Body Dimensions. Journal of Statistics Education 11(2).

```{r}
library(rmarkdown)
library(tidyverse)
library(viridis)
library(ggtext)
library(openintro)


```
Data with body measurements comes with the openintro package and called bdims
```{r}
data(bdims)
mean(bdims$wgt)
```
Now let's calculate BMI and save only females with normal weight meaning BMI <25
```{r}
bdims_bmi <- bdims %>%
  mutate(BMI = wgt / (hgt/100)^2) %>%
  filter(BMI < 25 )%>%
  filter(sex == 0 )
```
What's the distribution for chest, waist and hip girth
```{r}
ggplot(bdims_bmi, aes(x = che_gi)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black")+
  labs(title = "Circumference of the chest", x = "Chest girth in cm", y = "Frequency")

ggplot(bdims_bmi, aes(x = wai_gi)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black")+
  labs(title = "Circumference of the waist", x = "Waist girth in cm", y = "Frequency")

ggplot(bdims_bmi, aes(x = hip_gi)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black")+
  labs(title = "Circumference of the hips", x = "Hip girth in cm", y = "Frequency")


```
Now we will find out if 90-60-90 (+-1) appears in our dataset
```{r}
result <- bdims_bmi %>%
  filter(
    che_gi >= 89 & che_gi <= 91 &
      wai_gi >= 59 & wai_gi <= 61 &
      hip_gi >= 89 & hip_gi <= 91
  )
```
Print the decision
```{r}
if (nrow(result) > 0) {
  print("Rows with values within ±1 of the specified values exist in the dataset.")
} else {
  print("No rows with values within ±1 of the specified values exist in the dataset.")
}
```
Now we will find the most common values of che_gi and hip_gi that correspond to wai_gi values within the range of 59 to 61 cm
```{r}

common60 <- bdims_bmi %>%
        filter(wai_gi >= 59 & wai_gi <= 61)

mode_che_gi <- names(sort(table(common60$che_gi), decreasing = TRUE))[1]
mode_hip_gi <- names(sort(table(common60$hip_gi), decreasing = TRUE))[1]

mode_che_gi
mode_hip_gi

median_che_gi <- median(common60$che_gi)
median_hip_gi <- median(common60$hip_gi)

median_che_gi
median_hip_gi

mean_che_gi <- mean(common60$che_gi)
mean_hip_gi <- mean(common60$hip_gi)

mean_che_gi
mean_hip_gi

```
Rounded means, which are 79 anf 87, are equal to median values, and we will call them 'average'.

Time to plot!
```{r}

library(patchwork)

che_gi_value <- 90
wai_gi_value <- 60
hip_gi_value <- 90


plot1 <- ggplot(bdims_bmi, aes(x = che_gi)) +
        geom_histogram(binwidth = 1, fill = "#008080", color = "black") +
        geom_vline(xintercept = che_gi_value, color = "#FF69B4", linetype = "dashed", size = 2) +
        labs(title = stringr::str_wrap("Is <span style='color:#FF69B4'>90-60-90</span> a realistic idea of female body?"),
             subtitle = paste(stringr::str_wrap("Let's look at the body measurements of 215 physically active women with normal weight (BMI < 25). The histograms illustrate a wide distribution of body measurements. The bust circumference of 90 cm and waist circumference of 60 cm are uncommon. The analysis also shows that not a single woman had a 90-60-90 body shape. On average, women with a 60 cm waist typically have a bust measurement of 79 cm and a hip measurement of 87 cm. The 90-60-90 combination does not represent a common body shape."), "\n\n", "Bust Circumference" ),
             y = "Frequency")+
        theme_minimal() +
        theme(
                panel.border = element_blank(),
                text = element_text(size = 18, family = "Comic Sans MS"),
                legend.position = "top",
                panel.grid.major = element_blank(),  # Remove major gridlines
                panel.grid.minor = element_blank(),  # Remove minor gridlines
                axis.title.x = element_blank(),
                axis.text.x = element_text(face = "bold"),
                axis.title.y = element_blank(),
                plot.title = element_markdown(margin = margin(b = 15, t =30), face = "bold")
                )
plot1
plot2 <- ggplot(bdims_bmi, aes(x = wai_gi)) +
        geom_histogram(binwidth = 1, fill = "#008080", color = "black") +
        geom_vline(xintercept = wai_gi_value, color = "#FF69B4", linetype = "dashed", size = 2) +
        labs(subtitle = "Waist Circumference",
              y = "Number of individuals")+
        theme_minimal() +
        theme(
                panel.border = element_blank(),
                text = element_text(size = 18, family = "Comic Sans MS"),
                panel.grid.major = element_blank(),  # Remove major gridlines
                panel.grid.minor = element_blank(),  # Remove minor gridlines
                axis.title.x = element_blank(),
                axis.text.x = element_text(face = "bold"),
                axis.title.y = element_text(margin = margin(r = 15), face = "bold")
                )
plot2
plot3 <- ggplot(bdims_bmi, aes(x = hip_gi)) +
        geom_histogram(binwidth = 1, fill = "#008080", color = "black") +
        geom_vline(xintercept = hip_gi_value, color = "#FF69B4", linetype = "dashed", size = 2) +
        labs(subtitle = "Hip Circumference",
             x = "Measurments in cm",
             caption = "Heinz G, et al. 2003. Exploring Relationships in Body Dimensions|Created by Elena Shekhova")+
        theme_minimal() +
        theme(
                panel.border = element_blank(),
                text = element_text(size = 18, family = "Comic Sans MS"),
                panel.grid.major = element_blank(),  # Remove major gridlines
                panel.grid.minor = element_blank(),  # Remove minor gridlines
                axis.title.x = element_text(margin = margin(t = 15), face = "bold"),
                axis.text.x = element_text(face = "bold"),
                axis.title.y = element_blank(),
                plot.caption = element_text(size = 15, color = "#A9A9A9", hjust = 0.8,  margin = margin(t = 25, b = 30)))
plot3

combined_plots <- plot1 + plot2 + plot3 + plot_layout(ncol = 1)


combined_plots
ggsave("combined_plots.png", plot = combined_plots, width = 4000, height = 3000, units = "px", dpi = 300)

```
